### 2016-09-26 results.tex
making a pass through the results section, especially the lin, bi-lin, ds constructions

\begin{definition}
A set-multiplicity data structure $(\Rep, \Qry)$ is {\sf canonical} if
there exist algorithms $\Rep_1, \Rep_2$, and a function
$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
such that the following hold:
\begin{itemize}
\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
where $t$ depends only on~$n$.
\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
$\pubaux$.
\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
on $\pubaux$ computing as follows: 
(1) $s_1, \ldots, s_t \getsr \Rep_1(S)$;
(2) $K \getsr \calK$;
(3) $\pubaux \getsr \Rep_2(n, F_{K}(s_1), \ldots,F_{K}(s_t))$. 
%\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
%\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1),
%\ldots,F_{K_j}(s_t)\}_{j\in[p]})$. 
\end{itemize}
In this case, we say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
of~$\Rep$. \tsnote{Seems odd to call it this without explaining how
  this canonical representation handles $\privaux$, too.  }
\end{definition}
\jnote{Not sure how general to make the above. Need to verify that it is general enough
to prove security of all the constructions we care about.}
\tsnote{Would be good to give an example or two of the schemes this
  covers.  Domain-separated PRF BF, for example.  I think it covers
  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
  functions and does the hashing. (Although the following theorem does
  not work in this case, of course.) It does not cover
  linear-PRF or Neidermayer. }
We next show that any canonical data structure in which~$F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.

@@

\subsection{Linear PRF-hash construction }
%\heading{Linear-PRF construction. }
Here we consider a set-multiplicity data structure that was attacked
by Neidermayer et al. in~\cite{xxx}. \todo{Not actually a true
  statement, because $\Rep$ isn't correct.  Needs fixing.} Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).  The following result shows, informally, that if~$F$ is a good PRF, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.

@@

\begin{theorem}\label{thm:bi-lin-ss}
Let $\Pi_{\mathrm{bi-lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K_1},F_{K_2}$ replaced by independent random functions~$\rho_1,\rho_2$ (respectively).  Let $\leak$ be the leakage function just described.   Let~$\univ=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.  It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$,
the advantage $\AdvPrivSS{\Pi_{\mathrm{bi-lin}},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.

@@

On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab' as input.  It can perfectly simulate $M_1,M_2$ by lazily sampling random functions~$\rho_1,\rho_2$ itself.  However, it has no information about the bit~$z$, so at best it can cause~$A$ to output 1 with probabilility~$1/2$.
\end{proof}

>>>>

\begin{definition}
A set-multiplicity data structure $(\Rep, \Qry)$ is {\sf canonical} if
there exist algorithms $\Rep_1, \Rep_2$, and a function
$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
such that the following hold:
\begin{itemize}
\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
where $t$ depends only on~$n$.
\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
$\pubaux$.
\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
on $\pubaux$ computing as follows: 
(1) $s_1, \ldots, s_t \getsr \Rep_1(S)$;
(2) $K \getsr \calK$;
(3) $\pubaux \getsr \Rep_2(n, F_{K}(s_1), \ldots,F_{K}(s_t))$. 
%\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
%\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1),
%\ldots,F_{K_j}(s_t)\}_{j\in[p]})$. 
\end{itemize}
In this case, we say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
of~$\Rep$. \tsnote{Seems odd to call it this without explaining how
  this canonical representation handles $\privaux$, too.  }
\end{definition}
\jnote{Not sure how general to make the above. Need to verify that it is general enough
to prove security of all the constructions we care about.}
\tsnote{Point out an example or two of the schemes this
  covers.  Domain-separated PRF BF, for example.  I think it covers
  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
  functions and does the hashing. (Although the following theorem does
  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
We next show that any canonical data structure in which~$F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.

@@

\subsection{Linear PRF-hash Bloom Filter }
%\heading{Linear-PRF construction. }
The domain-separated PRF-hash requires~$k$ PRF evaluations per set-membership query, and this may be unattractive in certain use cases.  Kirsch and Mitzenmacher~\cite{xxx} have shown that two PRF evaluations suffices, defining the hash functions to be $h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle) \bmod m$, where~$m$ is the bitlength of the Bloom filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot F_{K_2}(x) \bmod m$, using distinct keys instead of domain-separation, but the constructions are equivalent with respect to security.} We call this the \emph{linear PRF-hash} Bloom Filter.  In this section, we show that this scheme is both correct and private with respect to our SS notion.

Looking ahead to the next section, we will analyze a closely related construction, which was attacked by Neidermayer et al.~\cite{xxx} in the context of private medical-record linkage.  It uses the same linear-PRF hash functions, but has a $\Rep$ algorithm that that does not ensure that the hash functions are called on \emph{distinct} values.  We show that this is \emph{not} private with respect to our SS notion for a leakage function that leaks nearly the entire set~$S$. \todo{It would be better, perhaps, to show that it is not OW secure, since this implies it isn't SS secure, and OW security is what Neidermayer et al. violate.}

Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).  The following result shows, informally, that if~$F$ is a good PRF, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.

@@

\begin{theorem}\label{thm:bi-lin-ss}
Let $\Pi_{\mathrm{bi-lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.  Let $\leak$ be the leakage function just described.   Let~$\univ=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.  It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$,
the advantage $\AdvPrivSS{\Pi_{\mathrm{bi-lin}},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.

@@

On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab' as input.  It can perfectly simulate $M_1,M_2$ by lazily sampling random function~$\rho$ itself.  However, it has no information about the bit~$z$, so at best it can cause~$A$ to output 1 with probabilility~$1/2$.
\end{proof}
